---
title: "Report feedback"
format: docx
editor: visual
writer: Jofrey Segeza Amos
---

```{r setup, include=FALSE}

# hide all code chunks in the output, but show errors 
     # nb. warnings and messages still shown
knitr::opts_chunk$set(echo = FALSE,  # hide all code chunks in output
                      error = TRUE,  # show errors if they appear, but don't stop (produce the word doc)
                      warning = FALSE, # do not show warnings in the output word doc 
                      message = FALSE, # do not show  messages in the output word doc
                      fig.width = 7,         # Figure width
                      fig.height = 7,        # Figure height
                      fig.topcaption = TRUE  # show figure titles on top of plot
                     )

source('Main.R')
```

## Overview of professional distributions across departments

T

**Table 01: Professional distributions**

```{r}
#| echo: false
figure01
```

## Relationship between stress level and mental health leave days taken.

Figure 02 : Relationship between

```{r}
figure02
```

## Basic healthcare workers characteristics in relation to stress level

**Table 01: Level of stress among healthcare workers**

```{r}
#| echo: false
table01
```

## Basic healthcare workers characteristics in relation to level of job satisfaction.

Table 02; Basic healthcare characteristics in terms of level of jobs satusfaction.

```{r}
#| echo: false
table02
```

**Table 04: Level of stress among different healthcare workers categorized according to level of job satisfaction.**

```{r}
#| echo: false
figure03
```

## Work induced depression

8Disclaimer; Criteria used are random picked criteria to fit in the simulation, are not clinical criteria and should not be used as a reference.

**Table 03: Employees with work-induced depression**

```{r}
#| echo: false
table03
```

Table 04 below elaborates about utilization of employees assistance programme and proportion of employees with work-induced depression who have had access to this service

**Table 04: Employees with work induced depression who had access to employee assisastance programme**

```{r}
#| echo: false
table04
```

## Logistic regression model 

A logistic regression model to determine the causal relationship between healthcare department, work related stress factor and work related stress level was developed. However reliability of these model couldn't be well established due to missing effect modifiers and clarity of confounding variables
