---
title: "Report feedback"
format: docx
editor: visual
writer: Jofrey Segeza Amos
---

```{r setup, include=FALSE}

# hide all code chunks in the output, but show errors 
     # nb. warnings and messages still shown
knitr::opts_chunk$set(echo = FALSE,  # hide all code chunks in output
                      error = TRUE,  # show errors if they appear, but don't stop (produce the word doc)
                      warning = FALSE, # do not show warnings in the output word doc 
                      message = FALSE, # do not show  messages in the output word doc
                      fig.width = 7,         # Figure width
                      fig.height = 7,        # Figure height
                      fig.topcaption = TRUE  # show figure titles on top of plot
                     )

source('Main.R')
```

## Overview of professional distributions across departments

T

**Table 01: Professional distributions**

```{r}
#| echo: false
figure01
```

## Relationship between stress level and mental health leave days taken.

Figure 02 : Relationship between

```{r}
figure02
```

## Basic healthcare workers characteristics in relation to stress level

**Table 01: Level of stress among healthcare workers**

```{r}
#| echo: false
table01
```

## Basic healthcare workers characteristics in relation to level of job satisfaction.

Table 02; Basic healthcare characteristics in terms of level of jobs satusfaction.

```{r}
#| echo: false
table02
```

**Table 04: Level of stress among different healthcare workers categorized according to level of job satisfaction.**

```{r}
#| echo: false
figure03
```

## Work induced depression

8Disclaimer; Criteria used are random picked criteria to fit in the simulation, are not clinical criteria and should not be used as a reference.

**Table 03: Employees with work-induced depression**

```{r}
#| echo: false
table03
```

Table 04 below elaborates about utilization of employees assistance programme and proportion of employees with work-induced depression who have had access to this service

**Table 04: Employees with work induced depression who had access to employee assisastance programme**

```{r}
#| echo: false
table04
```

## Self Esteem

Majority of the students, 206 (86%) had normal self esteem according to the Rosenberg Self-Esteem Scale (RSES) scores, however 32(13%) of all students had low self esteem.

Table 08; Scores of Rosenberg Self-Esteem Scale (RSES) among students

```{r}
#| echo: false
table08
```

## Social support

Only 43(18%) of all students had strong social support, while 96(40%) had poor social support according to the Oslo socila support score.

Table 09: Social support

```{r}
#| echo: false
table09
```

## Audit ; family history.

```{r}
#| echo: false
table041
```

**Figure 01: AUDIT family Hx**

## AUDIT ; dropping out.

```{r}
#| echo: false
table042
```

**Figure 02:**

## PHQ; Family Hx

```{r}
#| echo: false
table051
```

**Figure 03:**

## PHQ ; Dropping Out

```{r}
#| echo: false
table052
```

## 
